\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools,bm}
\usepackage{enumitem,booktabs,array}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage[protrusion=true,expansion=false]{microtype}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\setlist[itemize]{topsep=2pt,itemsep=2pt}
\setlist[enumerate]{topsep=2pt,itemsep=2pt}
\newtcolorbox{keybox}{colback=blue!3!white,colframe=blue!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{alertbox}{colback=red!3!white,colframe=red!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{answerbox}{colback=green!3!white,colframe=green!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{drillbox}{colback=yellow!5!white,colframe=orange!60!black,boxrule=0.4pt,arc=1mm}
\newcommand{\EV}{\mathbb{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\blank}[1]{\underline{\hspace{#1}}}

\title{E03-05: Erel, Stern, Tan \& Weisbach (2021, RFS) \\
\large ``Selecting Directors Using Machine Learning'' --- Active Recall Workbook}
\author{Empirical Corporate Finance II --- Exam Prep}
\date{\today}
\begin{document}\maketitle

\begin{keybox}
\textbf{Paper in one sentence.} Using machine learning (random forests) trained on director characteristics and subsequent firm outcomes, ESTW build a model that \emph{out-performs} actual board-director choices: had firms followed the model's recommendations, predicted poor performers would have been deselected, suggesting boards make systematic selection mistakes that data-driven methods could correct.

\textbf{Placement.} Pioneering application of ML to governance-selection questions. Connects corporate governance to the algorithmic-decision-making literature (Kleinberg et al.\ 2018).
\end{keybox}

\section*{Round 1: Complete Walk-Through}

\subsection*{1.1 Research design}
\begin{itemize}
\item Sample: US public-firm directors and CEOs 2000--2014.
\item Features: demographics, education, prior boards, industry experience, connections, past performance.
\item Target: future director-quality outcomes (e.g., shareholder votes against, probability of removal, firm-level misstatements).
\item Split sample; train random forest on early years, test on later years.
\end{itemize}

\subsection*{1.2 Model approach}
\begin{itemize}
\item Random forests and gradient-boosted trees predict whether a nominee will under-perform.
\item Compare to actual nomination outcomes.
\item Quantify: how many of the worst-10\% predicted directors were actually chosen?
\end{itemize}

\subsection*{1.3 Headline findings}
\begin{itemize}
\item Firms chose directors the model predicted would be in the worst decile $\sim$1.5--2x more often than would occur if ML-ranked.
\item Predicted ``bad'' directors are more likely to receive low shareholder votes, leave under pressure, and coincide with governance failures.
\item Improvement from using the model: replacing the bottom-10\% would reduce bad-director incidence by $\sim$15--20\%.
\end{itemize}

\subsection*{1.4 Mechanism / features}
\begin{itemize}
\item Predictive features: prior-board performance, network position, demographic fit to board.
\item Boards appear to over-weight easily-observed features (connections, CEO tenure) and under-weight predictive ones.
\item Suggests behavioral biases in director selection, not just noise.
\end{itemize}

\subsection*{1.5 Interpretation}
\begin{itemize}
\item Governance failures reflect selection errors as much as (or more than) monitoring effort.
\item ML can augment human judgment in board appointments.
\item Consistent with broader Kleinberg et al.\ (2018) result that algorithms improve on human prediction.
\end{itemize}

\subsection*{1.6 Caveats}
\begin{alertbox}
\begin{itemize}
\item Training targets are imperfect proxies for director quality.
\item External validity: test-sample features change over time.
\item Potential legal/ethical concerns about algorithmic director selection.
\end{itemize}
\end{alertbox}

\section*{Round 2: Level 1 Fill-in}
\begin{enumerate}
\item Method: \blank{2cm} forests on director features.
\item Sample: US directors \blank{1cm}--\blank{1cm}.
\item Target: predicted \blank{2cm} performance.
\item Finding: firms chose predicted-bad directors \blank{1cm}x more than random.
\item Gain: replacing bottom 10\% reduces bad incidence by \blank{1cm}--\blank{1cm}\%.
\end{enumerate}

\section*{Round 3: Level 2 Prompts}
\begin{enumerate}
\item Describe the training/testing ML design.
\item Report the main predictive performance findings.
\item Discuss what features drive under-performance predictions.
\item Relate ESTW to Kleinberg et al.\ (2018) and the algorithmic-judgment literature.
\item Evaluate ethical and legal implications of ML-based director selection.
\end{enumerate}

\section*{Round 4: Minimal Scaffolding}
From a blank page: (i) design, (ii) model, (iii) key finding, (iv) mechanism, (v) interpretation.

\section*{Round 5: Blank Page}
Essay: can machine learning improve board-director selection?

\vspace{6pt}
\begin{drillbox}
\textbf{Speed Drill.} (1) Method. (2) Training data. (3) Target variable. (4) Main finding. (5) Policy implication.
\end{drillbox}

\section*{Quick Reference \& Answer Key}
\begin{answerbox}
\begin{itemize}
\item \textbf{Method.} Random forests on director features.
\item \textbf{Target.} Director-quality outcomes.
\item \textbf{Finding.} Firms pick predicted-bad directors $\sim$2x more than random.
\item \textbf{Gain.} Replace bottom 10\% $\to$ $-15$--$20$\% bad incidence.
\end{itemize}
\end{answerbox}

\begin{keybox}
\textbf{30-second exam pitch.} Erel, Stern, Tan \& Weisbach (2021) apply machine learning (random forests, gradient-boosted trees) to the problem of director selection. Using US public-firm director data 2000--2014, with features including demographics, education, network position, prior-board experience, and targets including future low shareholder-vote receipt, misstatement likelihood, and forced turnover, they show that firms disproportionately select directors whom the model predicts will under-perform --- roughly $1.5$--$2\times$ more often than random, with gains from replacing the bottom-10\% predicted of $\sim$15--20\%. Boards appear to over-weight easily-observed features (connections, CEO tenure) and under-weight predictive ones. The paper extends Kleinberg et al.\ (2018)'s algorithms-beat-humans result to corporate governance: governance failures reflect selection errors as much as monitoring effort, and data-driven methods can augment director selection. It raises normative questions about algorithmic governance decisions.
\end{keybox}

\end{document}
