\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools,bm}
\usepackage{enumitem,booktabs,array}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage[protrusion=true,expansion=false]{microtype}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\setlist[itemize]{topsep=2pt,itemsep=2pt}
\setlist[enumerate]{topsep=2pt,itemsep=2pt}
\newtcolorbox{keybox}{colback=blue!3!white,colframe=blue!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{alertbox}{colback=red!3!white,colframe=red!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{answerbox}{colback=green!3!white,colframe=green!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{drillbox}{colback=yellow!5!white,colframe=orange!60!black,boxrule=0.4pt,arc=1mm}
\newcommand{\EV}{\mathbb{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\blank}[1]{\underline{\hspace{#1}}}

\title{E06-03: Li, Taylor \& Wang (2018, JFE) \\
\large ``Inefficiencies and Externalities from Opportunistic Acquirers'' --- Active Recall Workbook}
\author{Empirical Corporate Finance II --- Exam Prep}
\date{\today}
\begin{document}\maketitle

\begin{keybox}
\textbf{Paper in one sentence.} LTW identify ``opportunistic acquirers'' --- firms that buy underperforming targets more for managerial/agency reasons than for synergy --- and show that their deals underperform, create negative externalities on peer firms in the target's industry (by depressing peer prices), and that these inefficiencies concentrate in industries with weak governance.

\textbf{Placement.} Agency-cost side of the M\&A debate; complements Harford-style wave studies with evidence that some M\&A is value-destroying and has spillover effects on competitors.
\end{keybox}

\section*{Round 1: Complete Walk-Through}

\subsection*{1.1 Motivation}
If M\&A is always efficient reallocation (Maksimovic-Phillips), why do many acquirers underperform? LTW model ``opportunistic'' acquirers who pursue deals that benefit managers (e.g., empire-building, entrenchment) rather than shareholders, and quantify the resulting inefficiency.

\subsection*{1.2 Identification of opportunistic deals}
\begin{itemize}
\item Define an acquirer as opportunistic when pre-deal governance is weak, target is poorly matched on synergy proxies, and announcement CAR is significantly negative.
\item Alternatively, use deal-level characteristics: diversifying, cash-financed, high market-to-book acquirer buying low market-to-book target without product-market link.
\item Classify with a probabilistic model of deal quality.
\end{itemize}

\subsection*{1.3 Data and design}
\begin{itemize}
\item SDC M\&A 1990--2014; CRSP returns; Compustat fundamentals.
\item Peer firms identified via SIC or TNIC.
\item Cross-sectional regressions of acquirer and peer CARs and long-run operating performance on opportunistic-deal indicators.
\end{itemize}

\subsection*{1.4 Headline results}
\begin{itemize}
\item Opportunistic acquirers show significant negative long-run operating performance (ROA $-2$ to $-3$ pp over 3 years).
\item Peers of opportunistic acquirers earn negative abnormal returns at deal announcement (spillover).
\item Weak-governance firms are much more likely to engage in opportunistic deals.
\item Classification model is predictive out-of-sample: top-quartile predicted-opportunistic deals have lower acquirer and peer returns.
\end{itemize}

\subsection*{1.5 Mechanism}
\begin{itemize}
\item Opportunistic consolidation can reduce competitive discipline on peers (if synergies absent but scale rises), lowering industry-wide efficiency.
\item Alternatively, poor deals signal negative information about industry prospects.
\item Weak governance enables managerial entrenchment via value-destroying M\&A.
\end{itemize}

\subsection*{1.6 Implications}
\begin{itemize}
\item M\&A is not uniformly efficient; agency-motivated deals coexist with synergy-driven ones.
\item Peers bear costs of opportunistic deals; externalities warrant governance scrutiny.
\item Governance reforms can reduce value-destroying M\&A.
\end{itemize}

\subsection*{1.7 Caveats}
\begin{alertbox}
\begin{itemize}
\item Opportunism classification is model-dependent.
\item Peer-firm CARs may reflect revaluation rather than externality.
\item Pre-deal-governance endogenous to prior management decisions.
\end{itemize}
\end{alertbox}

\section*{Round 2: Level 1 Fill-in}
\begin{enumerate}
\item Opportunistic acquirer: weak \blank{2cm}, poor synergy match.
\item Acquirer long-run ROA: $-$\blank{1cm} to $-$\blank{1cm} pp.
\item Peer-firm CARs: \blank{1cm} abnormal returns.
\item Deals concentrated in \blank{2cm} industries.
\item Implication: governance reduces value-\blank{2cm} M\&A.
\end{enumerate}

\section*{Round 3: Level 2 Prompts}
\begin{enumerate}
\item Define opportunistic acquirers and discuss identification.
\item Report main findings on acquirer, peer, and long-run performance.
\item Discuss the externality mechanism.
\item Contrast LTW with Maksimovic-Phillips and Harford views.
\item What governance reforms follow from the findings?
\end{enumerate}

\section*{Round 4: Minimal Scaffolding}
From a blank page: (i) motivation, (ii) identification, (iii) findings, (iv) externality, (v) policy.

\section*{Round 5: Blank Page}
Essay: opportunistic M\&A, externalities, and governance.

\vspace{6pt}
\begin{drillbox}
\textbf{Speed Drill.} (1) Classification. (2) Acquirer performance. (3) Peer performance. (4) Industry pattern. (5) Policy.
\end{drillbox}

\section*{Quick Reference \& Answer Key}
\begin{answerbox}
\begin{itemize}
\item \textbf{Def.} Weak-governance + poor-synergy deals.
\item \textbf{Acquirer.} Negative long-run ROA.
\item \textbf{Peer.} Negative CARs at announcement.
\item \textbf{Lesson.} Value-destroying M\&A has externalities.
\end{itemize}
\end{answerbox}

\begin{keybox}
\textbf{30-second exam pitch.} Li, Taylor \& Wang (2018) identify ``opportunistic acquirers'' --- firms that pursue value-destroying M\&A driven by agency motives rather than synergy --- and show the resulting inefficiency spreads to competitors. Using SDC mergers 1990--2014 with a classification based on governance weakness, poor synergy fit, and negative announcement CARs, they find opportunistic deals exhibit significant negative long-run acquirer ROA ($-2$ to $-3$ pp over 3 years), peer firms in the target's industry suffer negative announcement-window abnormal returns, and such deals concentrate in weak-governance industries. The classification predicts underperformance out of sample. The paper formalizes the agency-cost side of M\&A --- complementing Maksimovic-Phillips (efficient reallocation) and Harford (2005) (wave timing) with evidence that agency-motivated deals impose externalities on peer firms, giving a clear governance rationale for scrutinizing manager-serving acquisitions.
\end{keybox}

\end{document}
