\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools,bm}
\usepackage{enumitem,booktabs,array}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage[protrusion=true,expansion=false]{microtype}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\setlist[itemize]{topsep=2pt,itemsep=2pt}
\setlist[enumerate]{topsep=2pt,itemsep=2pt}
\newtcolorbox{keybox}{colback=blue!3!white,colframe=blue!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{alertbox}{colback=red!3!white,colframe=red!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{answerbox}{colback=green!3!white,colframe=green!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{drillbox}{colback=yellow!5!white,colframe=orange!60!black,boxrule=0.4pt,arc=1mm}
\newcommand{\EV}{\mathbb{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\blank}[1]{\underline{\hspace{#1}}}

\title{W08-04: Dewally, Ederington \& Fernando (2013, RFS) \\
\large ``Determinants of Trader Profits in Commodity Futures Markets'' --- Active Recall Workbook}
\author{Banking \& Risk Management --- Exam Prep}
\date{\today}
\begin{document}\maketitle

\begin{keybox}
\textbf{Paper in one sentence.} Using unique trader-level CFTC data, DEF document that commodity producers (hedgers) \emph{lose} money to speculators on average: hedgers pay an insurance premium of $\approx 1$--$3\%$ per year, and the premium is higher when producers are more financially constrained --- a trader-level empirical counterpart of the Acharya-Lochstoer-Ramadorai risk-premium story.

\textbf{Placement.} Companion to W08-03 (ALR 2013): same hedging-pressure narrative but using \emph{trader-level} P\&L rather than commodity futures returns. Directly tests who bears the cost of hedging.
\end{keybox}

\section*{Round 1: Complete Walk-Through}

\subsection*{1.1 Data and scope}
Non-public CFTC trader-level positions and P\&L in US crude oil, natural gas, heating oil, and gasoline futures 2003--2008. Traders classified by CFTC as hedgers (commercial) or speculators (non-commercial).

\subsection*{1.2 Central quantities}
\begin{itemize}
\item Hedger average P\&L per year, normalised by size of hedging position.
\item Speculator average P\&L, similarly normalised.
\item Dispersion in P\&L across trader type.
\end{itemize}

\subsection*{1.3 Headline results}
\begin{itemize}
\item Hedgers (commercials) lose on average $\sim 1$--$3\%$ per year on their futures positions; speculators earn a symmetric positive return --- consistent with producers paying an \emph{insurance premium}.
\item Losses are larger for more financially constrained hedgers: firms with higher leverage, lower credit ratings, or higher default probability pay more.
\item Within speculators, commodity-specialist traders earn the highest profits; index investors earn much less.
\item Effects are robust to alternative measures of position size and to controlling for market conditions.
\end{itemize}

\subsection*{1.4 Interpretation}
\begin{itemize}
\item Direct trader-level evidence for the hedging-pressure theory of commodity risk premia.
\item Hedgers willingly pay an insurance premium, consistent with Froot--Scharfstein--Stein rationale.
\item Speculators who can absorb price risk earn the premium; capital-constrained speculators leave money on the table.
\end{itemize}

\subsection*{1.5 Caveats}
\begin{alertbox}
\begin{itemize}
\item CFTC data are proprietary; replication constrained.
\item Hedger/speculator classification is imperfect.
\item Short sample (2003--2008) includes a boom and crash; dynamics may not generalise.
\end{itemize}
\end{alertbox}

\section*{Round 2: Level 1 Fill-in}
\begin{enumerate}
\item Data: trader-level CFTC positions and \blank{1cm}.
\item Hedger average P\&L sign: \blank{1cm}; magnitude: \blank{1cm}--\blank{1cm}\%/yr.
\item Most profitable speculator type: \blank{2cm} specialist.
\item More constrained hedgers pay \blank{1cm} insurance premium.
\item Sample years: \blank{1cm}--\blank{1cm}.
\end{enumerate}

\section*{Round 3: Level 2 Prompts}
\begin{enumerate}
\item Why is an average hedger loss consistent with rational hedging?
\item Which specification identifies ``constraint makes premium larger''?
\item Connect DEF to ALR (W08-03): what does each paper add?
\item Does DEF's evidence support or contradict Allayannis--Weston (2001)?
\end{enumerate}

\section*{Round 4: Minimal Scaffolding}
From a blank page: (i) data, (ii) central comparison, (iii) magnitudes, (iv) constraint interaction, (v) two caveats.

\section*{Round 5: Blank Page}
Essay: hedgers, speculators, and the price of commodity insurance.

\vspace{6pt}
\begin{drillbox}
\textbf{Speed Drill.} (1) Data type. (2) Hedger P\&L sign and magnitude. (3) Most profitable speculator subclass. (4) Constraint effect. (5) Sample years.
\end{drillbox}

\section*{Quick Reference \& Answer Key}
\begin{answerbox}
\begin{itemize}
\item \textbf{Data.} Trader-level CFTC positions and P\&L in energy commodities.
\item \textbf{Hedgers.} Lose $\sim 1$--$3\%$/yr on futures --- an insurance premium.
\item \textbf{Constraint.} More constrained hedgers pay more.
\item \textbf{Speculators.} Specialists earn; index investors earn less.
\end{itemize}
\end{answerbox}

\begin{keybox}
\textbf{30-second exam pitch.} Dewally, Ederington \& Fernando (2013) test the hedging-pressure theory at the trader level. Using CFTC position and P\&L data for energy-futures traders 2003--2008, they show that commercial hedgers lose on average 1--3\% per year on their futures exposure --- a clear insurance premium paid to speculators. Losses are larger for hedgers with more financial constraints (higher leverage, higher default probability), consistent with Froot--Scharfstein--Stein logic that willingness to pay for insurance rises with distress cost. Speculator earnings mirror hedger losses; commodity-specialist speculators capture more than passive index investors. The paper is the trader-level counterpart to Acharya--Lochstoer--Ramadorai (2013): both confirm that hedging-pressure / limits-to-arbitrage shape commodity risk premia and that capital-constrained producers pay more for insurance.
\end{keybox}

\end{document}
