\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools,bm}
\usepackage{enumitem,booktabs,array}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage[protrusion=true,expansion=false]{microtype}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\setlist[itemize]{topsep=2pt,itemsep=2pt}
\setlist[enumerate]{topsep=2pt,itemsep=2pt}
\newtcolorbox{keybox}{colback=blue!3!white,colframe=blue!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{alertbox}{colback=red!3!white,colframe=red!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{answerbox}{colback=green!3!white,colframe=green!40!black,boxrule=0.4pt,arc=1mm}
\newtcolorbox{drillbox}{colback=yellow!5!white,colframe=orange!60!black,boxrule=0.4pt,arc=1mm}
\newcommand{\EV}{\mathbb{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\blank}[1]{\underline{\hspace{#1}}}

\title{W08-01: Jin \& Jorion (2006, JF) \\
\large ``Firm Value and Hedging: Evidence from U.S.\ Oil and Gas Producers'' --- Active Recall Workbook}
\author{Banking \& Risk Management --- Exam Prep}
\date{\today}
\begin{document}\maketitle

\begin{keybox}
\textbf{Paper in one sentence.} In a sample of 119 US oil-and-gas producers 1998--2001, JJ find that \emph{hedging reduces a firm's stock-price sensitivity to oil and gas prices} as theory predicts, but \emph{does not raise firm value} (no Allayannis--Weston-style hedging premium in this industry) --- so hedging-value evidence is industry-specific.

\textbf{Placement.} Canonical rebuttal/complement to Allayannis--Weston (W07-04): same design, different industry, opposite Tobin's-Q result. Highlights the need to interpret hedging premia cautiously.
\end{keybox}

\section*{Round 1: Complete Walk-Through}

\subsection*{1.1 Setting}
US oil-and-gas (O\&G) producers 1998--2001. Firms hedge with forwards, swaps, and options on oil and gas prices. Hedging intensity hand-collected from 10-K filings --- notional amount relative to expected production.

\subsection*{1.2 Central tests}
\textbf{Test 1 (sensitivities).} Regress daily stock returns on oil and gas price returns, interacted with hedge ratio:
\[
r_{it}=\alpha_i+(\beta_{oi}+\gamma_o H_{it})\cdot r^o_t+(\beta_{gi}+\gamma_g H_{it})\cdot r^g_t+\varepsilon_{it}.
\]
Expected: $\gamma_o,\gamma_g<0$ --- hedging \emph{reduces} exposure.

\textbf{Test 2 (value).} Allayannis--Weston-style Tobin's Q regression:
\[
Q_{it}=\alpha + \beta\cdot H_{it}+X_{it}'\gamma+\varepsilon_{it}.
\]
Expected under AW logic: $\beta>0$ hedging premium.

\subsection*{1.3 Headline results}
\begin{itemize}
\item Hedging reduces stock price sensitivity roughly one-for-one with reported hedge ratios: the sensitivity test works.
\item \emph{No} Tobin's-Q hedging premium: $\beta$ is small and statistically zero --- sometimes even slightly negative.
\item Robust to alternative hedge-intensity measures, FE, and controls.
\end{itemize}

\subsection*{1.4 Interpretation}
\begin{itemize}
\item In a single-industry sample, investors can undo commodity risk themselves; hedging saves little on financial-distress cost at the margin.
\item AW's cross-industry estimate may reflect an endogenous bundling of hedging with other good governance traits; in a more homogeneous sample this disappears.
\item O\&G hedging does what the textbook says --- reduces exposure --- but does \emph{not} mechanically raise Q.
\end{itemize}

\subsection*{1.5 Caveats}
\begin{alertbox}
\begin{itemize}
\item Single-industry, short panel: power to detect a premium is limited.
\item Hedge ratio is partially endogenous to firm characteristics (leverage, investment).
\item Time-series is short (4 years); if premium is volatile, JJ may miss it.
\end{itemize}
\end{alertbox}

\section*{Round 2: Level 1 Fill-in}
\begin{enumerate}
\item Sample: $n=\blank{1cm}$ O\&G producers, \blank{1cm}--\blank{1cm}.
\item Test 1 expected sign on $\gamma$: \blank{1cm}.
\item Hedging-premium coefficient $\beta$: approximately \blank{1cm}.
\item Interpretation vs.\ AW: premium is \blank{2cm}-specific.
\item Canonical comparison paper: Allayannis--\blank{1.5cm} (2001).
\end{enumerate}

\section*{Round 3: Level 2 Prompts}
\begin{enumerate}
\item Write the interacted-sensitivity regression and state what each coefficient measures.
\item Why might AW find a premium across industries but JJ not find one within O\&G?
\item What does the JJ result imply about the ``hedging raises Q because it lowers distress cost'' argument?
\item Design a JJ-style test using a different industry (airlines, banks).
\end{enumerate}

\section*{Round 4: Minimal Scaffolding}
From a blank page: (i) sample, (ii) two tests, (iii) sensitivity result, (iv) value result, (v) interpretation.

\section*{Round 5: Blank Page}
Essay: does corporate hedging create value? Contrast AW (2001) and JJ (2006).

\vspace{6pt}
\begin{drillbox}
\textbf{Speed Drill.} (1) Industry. (2) Sample size. (3) Sensitivity-test sign. (4) Hedging-premium value. (5) Comparison paper.
\end{drillbox}

\section*{Quick Reference \& Answer Key}
\begin{answerbox}
\begin{itemize}
\item \textbf{Industry.} US oil-and-gas producers.
\item \textbf{Sensitivity test.} $\gamma<0$: hedging reduces exposure as expected.
\item \textbf{Value test.} $\beta\approx 0$: no Tobin's-Q hedging premium.
\item \textbf{Lesson.} AW's cross-industry premium is not universal.
\end{itemize}
\end{answerbox}

\begin{keybox}
\textbf{30-second exam pitch.} Jin \& Jorion (2006) run the Allayannis--Weston hedging-premium test in a clean single-industry setting: 119 US oil-and-gas producers, 1998--2001. The sensitivity test confirms that hedging does reduce stock-price exposure to oil and gas prices roughly one-for-one with reported hedge ratios. The value test is the surprise: no hedging premium in Tobin's Q. Investors can hedge commodity risk themselves when they hold a portfolio of O\&G firms, and the incremental financial-distress benefit of firm-level hedging is small. The JJ result disciplines the AW cross-industry premium: hedging does what it says on the tin --- lowers risk --- but does not mechanically lift valuation in industries where risk can be undone at the investor level. The sensible read is that AW's premium bundles hedging with other governance attributes.
\end{keybox}

\end{document}
